RNA-seq from 4 cell populations

### 2021-08-04 deconvolution/fans4/molec_profiling.Rmd
bug fix

  data.frame( EnsID = rownames(B.hat)[j], 
    Isq = fit$I2, 
    Hsq = fit$H2, 
    p.het = fit$QEp)
  },mc.cores = 12)
df_het = do.call(rbind, df_het)

@@

res_het[res_het$FDR < 0.05] %>% kable() %>% kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

@@

>>>>

  data.frame( EnsID = rownames(B.hat)[j], 
    Isq = fit$I2, 
    Hsq = fit$H2, 
    p.het = fit$QEp)
  },mc.cores = 12)
df_het = data.table(do.call(rbind, df_het))

df_hugo = AnnotationDbi::select(org.Hs.eg.db, df_het$EnsID, "SYMBOL", "ENSEMBL")
df_het = merge(df_het, df_hugo, by.x="EnsID", by.y = "ENSEMBL")
df_het$SYMBOL[is.na(df_het$SYMBOL)] = df_het$EnsID[is.na(df_het$SYMBOL)]

@@

res_het[res_het$FDR < 0.05,] %>% kable() %>% kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

@@

```{r plot.hetero, fig.height=30}

plotEffectSize = function(CellType, beta, se, main=''){

  df = data.frame(CellType, beta, se)

  ggplot(df, aes(CellType, beta, ymin = beta - 1.96*se, ymax = beta + 1.96*se, color=CellType)) + geom_point() + geom_errorbar(width=.1) + theme_classic() + theme(aspect.ratio=1, legend.position="none", plot.title = element_text(hjust = 0.5)) + coord_flip() + ylab(bquote(log[2]~FC)) + scale_color_manual(values = colorCodes[df$CellType]) + geom_hline(yintercept=0, linetype="dashed") + ggtitle(main)
}

figList = lapply( 1:10, function(k){

  j = order(df_het$p.het)[k]
  ensID = df_het$EnsID[j]
  geneID = df_het$SYMBOL[j]

  main = paste0(geneID, ' (', ensID, ")\nHeterogeneity (p=", format(df_het$p.het[j], digits=2), ')')

  fig1 = plotEffectSize( colnames(B.hat),
    B.hat[ensID,],
    se.hat[ensID,],
    main)

  main = paste0(geneID, ' (', ensID, ")\nHeterogeneity (p=", format(df_het$p.het[j], digits=2), ')')

  fig2 = plotEffectSize( colnames(resMash$result$PosteriorMean),
    resMash$result$PosteriorMean[ensID,],
    resMash$result$PosteriorSD[ensID,],
    main)

  plot_grid(fig1, fig2)
})
plot_grid(plotlist = figList, ncol=1)
```
